---
params:
  databaseId: "MDCR"
  targetId: 739138
  comparatorId: 715259
  outcomeId: 18
  setTitle: "Stroke risk in new-users of sertaline versus duloxetine for major depressive disorder in the MDCR database."
title: "`r params$setTitle`"
# Corresponding author: Martijn J. Schuemie, Janssen R&D, 1125 Trenton Harbourton Road, Titusville, NJ, 08560, Phone: +31 631793897, schuemie@ohdsi.org
author:
    
  - name: Martijn J. Schuemie
    affiliation: a,b,c
  - name: Patrick B. Ryan
    affiliation: a,b,d
  - name: Seng Chan You
    affiliation: a,e
  - name: Nicole Pratt
    affiliation: a,f
  - name: David Madigan
    affiliation: a,g
  - name: George Hripcsak
    affiliation: a,d
  - name: Marc A. Suchard
    affiliation: a,c,h,i
address:
  - code: a
    address: Observational Health Data Sciences and Informatics, New York, NY, USA
  - code: b
    address: Janssen Research & Development, Titusville, NJ, USA
  - code: c
    address: Department of Biostatistics, University of Califoria, Los Angeles, CA
  - code: d
    address: Department of Biomedical Informatics, Columbia University, New York, NY     
  - code: e
    address: Department of Biomedical Informatics, Ajou University, Suwon, South Korea
  - code: f
    address: Sansom Institute, University of South Australia, Adelaide SA, Australia
  - code: g
    address: Department of Statistics, Columbia University, New York, NY
  - code: h
    address: Department of Biomathematics, University of Califoria, Los Angeles, CA
  - code: i
    address: Department of Human Genetics, University of Califoria, Los Angeles, CA
lead_author_surname: Schuemie et al.
doi: "https://cran.r-project.org/package=YourPackage"
abstract: |
  Your abstract will be typeset here, and used by default a visually distinctive font.
  An abstract should explain to the general reader the major contributions of the article.
# Optional: Acknowledgements
acknowledgements: |
  This template package builds upon, and extends, the work of the excellent
  gratefully acknowledged as this work would not have been possible without them.  Our extensions
  are under the same respective licensing term
  [rticles](https://cran.r-project.org/package=rticles) package, and both packages rely on the
  [PNAS LaTeX](http://www.pnas.org/site/authors/latex.xhtml) macros. Both these sources are
  ([GPL-3](https://www.gnu.org/licenses/gpl-3.0.en.html) and
  [LPPL (>= 1.3)](https://www.latex-project.org/lppl/)).
# Optional: One or more keywords
keywords:
  - one
  - two
  - optional
  - keywords
  - here
papersize: letter
fontsize: 9pt
# Optional: Force one-column layout, default is two-column
# one_column: true
# Optional: Enables lineno mode, but only if one_column mode is also true
#lineno: true
# Optional: Enable one-sided layout, default is two-sided
#one_sided: true
# Optional: Enable section numbering, default is unnumbered
#numbersections: true
# Optional: Specify the depth of section number, default is 5
#secnumdepth: 5
# Optional: Skip inserting final break between acknowledgements, default is false
skip_final_break: true
# Optional: Bibliography
bibliography: bibliography.bib
# Optional: Enable a 'Draft' watermark on the document
watermark: true
footer_contents: "LEGEND Project Document"
output: pinp::pinp
# Required: Vignette metadata for inclusion in a package.
vignette: >
  %\VignetteIndexEntry{YourPackage-vignetteentry}
  %\VignetteKeywords{YourPackage, r, anotherkeyword}
  %\VignettePackage{YourPackage}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

## Introduction

This *pinp is not PNAS* template started when the introduction to
[Rcpp](http://dirk.eddelbuettel.com/code/rcpp.html) by \cite{PeerJ:Rcpp}
was converted into this updated
[Rcpp Introduction](https://eddelbuettel.github.io/pinp/Rcpp-introduction.pdf)
vignette.  It is based on the
[pnas_article](https://github.com/rstudio/rticles/tree/master/inst/rmarkdown/templates/pnas_article)
template of the wonderful [rticles](https://cran.r-project.org/package=rticles) package by
\cite{CRAN:rticles}. The conversion from markdown to latex is facilitated by
[rmarkdown](https://cran.r-project.org/package=rmarkdown)
\citep{CRAN:rmarkdown} and [knitr](https://cran.r-project.org/package=knitr)
\citep{CRAN:knitr}. The underlying LaTeX macros are from
[pnas.org](http://www.pnas.org/site/authors/latex.xhtml).

The remainder of the document carries over from the corresponding
[pnas_article](https://github.com/rstudio/rticles/tree/master/inst/rmarkdown/templates/pnas_article)
template document. but has been edited and updated to our use case.  A
few specific tips follow.  In general, for fine-tuning some knowledge
of LaTeX is helpful.

<!-- Read in analysis data -->

```{r, echo=FALSE, message=FALSE, comment=FALSE, results='hide'}
library(DatabaseConnector)
library(CohortMethod)
library(Legend)
library(knitr)
library(xtable)
library(ggplot2)
source("DataPulls.R")
source("PlotsAndTables.R")
options(knitr.kable.NA = '')

# params <- list(databaseId = "MDCR",
#                targetId = 739138,
#                comparatorId =  715259,
#                outcomeId = 18)

useStoredObject <- TRUE

if (!useStoredObject) {
    connectionDetails <- createConnectionDetails(dbms = "postgresql",
                                                 server = "localhost/ohdsi",
                                                 user = "postgres",
                                                 password = Sys.getenv("pwPostgres"),
                                                 schema = "legend")
    connection <- connect(connectionDetails)
    targetName <- getExposureName(connection, params$targetId)
    comparatorName <- getExposureName(connection, params$comparatorId)
    outcomeName <- getOutcomeName(connection, params$outcomeId)
    analyses <- getAnalyses(connection)
    mainResults <- getMainResults(connection,
                                  targetIds = params$targetId,
                                  comparatorIds = params$comparatorId,
                                  outcomeIds = params$outcomeId,
                                  databaseIds = params$databaseId)

    attrition <- getAttrition(connection,
                              targetId = params$targetId,
                              comparatorId = params$comparatorId,
                              outcomeId = params$outcomeId,
                              analysisId = 1,
                              databaseId = params$databaseId)

    balance <- getCovariateBalance(connection,
                                   targetId = params$targetId,
                                   comparatorId = params$comparatorId,
                                   databaseId = params$databaseId)

    ps <- getPs(connection,
                targetId = params$targetId,
                comparatorId = params$comparatorId,
                databaseId = params$databaseId)

    kaplanMeier <- getKaplanMeier(connection,
                                  targetId = params$targetId,
                                  comparatorId = params$comparatorId,
                                  outcomeId = params$outcomeId,
                                  databaseId = params$databaseId,
                                  analysisId = 2)
} else {
    load("paperData.rda")
}
```

## Methods

## Results

Table \ref{tab:demographics} \ldots

\clearpage

\begin{figure*}
\caption{\textbf{Patient demographics.} Target (T) population is sertaline new-users.  Comparative (C) population is dulexotine new-users.  We report the standardized difference of population means (StdDiff) before and after stratification for selected base-line patient characteristics.}\label{tab:demographics}
\begin{center}
\resizebox{0.5\textwidth}{!}{
\begin{tabular}{lrrrrrr}
\hline
& \multicolumn{3}{c}{Before stratification}
& \multicolumn{3}{c}{After stratification} \\
\multicolumn{1}{c}{Characteristic}
  & \multicolumn{1}{c}{T (\%)}
  & \multicolumn{1}{c}{C (\%)}
  & \multicolumn{1}{c}{StdDiff}
  & \multicolumn{1}{c}{T (\%)}
  & \multicolumn{1}{c}{C (\%)}
  & \multicolumn{1}{c}{StdDiff} \\
  \hline
```{r, echo=FALSE, results="asis", cache=TRUE}
table <- prepareTable1(balance)
table <- table[3:nrow(table),]

print(xtable(table, format = "latex", align = c("l","l","r","r","r","r","r","r")),
      include.rownames = FALSE,
      include.colnames = FALSE,
      hline.after = NULL,
      only.contents = TRUE,
      sanitize.text.function = identity)
```
\end{tabular}
}
\end{center}
\end{figure*}

\clearpage

```{r, echo=FALSE, cache=TRUE}
plot <- plotPs(ps, targetName, comparatorName)
suppressMessages(ggsave("ps.pdf", plot,
                        width = 5, height = 5, units = "in"))
```

\begin{figure}
  \centerline{
    \includegraphics[width=0.4\textwidth]{ps}
  }
  \caption{\textbf{Preference score distribution for sertaline and dulexotine new-users.}
  The preference score is a transformation of the propensity score that adjusts for size differences between populations.  A higher overlap indicates that subjects in the two populations are more similar in terms of their predicted probability of receiving one treatment over the other.
  }
\end{figure}

More text here.

\begin{figure}
\begin{tabular}{lrrrr}
```{r, echo=FALSE, results="asis"}
table <- mainResults
table$hr <- sprintf("%.2f (%.2f - %.2f)", mainResults$rr, mainResults$ci95lb, mainResults$ci95ub)
table$p <- sprintf("%.2f", table$p)
table$calHr <- sprintf("%.2f (%.2f - %.2f)", mainResults$calibratedRr, mainResults$calibratedCi95Lb, mainResults$calibratedCi95Ub)
table$calibratedP <- sprintf("%.2f", table$calibratedP)
table <- merge(table, analyses)
table <- table[, c("description", "hr", "p", "calHr", "calibratedP")]

print(xtable(table),
      include.rownames = FALSE,
      include.colnames = FALSE,
      hline.after = NULL,
      only.contents = TRUE,
      sanitize.text.function = identity)
```
\end{tabular}
\end{figure}


## Discussion

## Appendix

```{r, echo=FALSE, cache=TRUE}
plot <- drawAttritionDiagram(attrition, targetName, comparatorName)
suppressMessages(ggsave("attrition.pdf", plot,
                        width = 6, height = 10, units = "in"))
```

\begin{figure*}
  \begin{center}
    \includegraphics[width=0.66\textwidth]{attrition}
  \end{center}
  \caption{Attrition diagram for selecting new-users of }\label{fig:attrition}
\end{figure*}

## Inline R Code

The PNAS sample included a fixed PNG image here, but this document prefers
to show the results and embedding of _R_ code.

```{r figex, fig.width=3, fig.height=3, cache=TRUE, echo=TRUE, fig.cap="Narrow ggplot2 figure"}
library(ggplot2)
ggplot(mtcars, aes(wt, mpg)) +
    geom_point(size=3, aes(colour=factor(cyl))) +
    theme(legend.position="none")
```

Here we use a standard knitr bloc with explicit options for

- figure width and height (`fig.width`, `fig.height`), both set to three inches;
- whether the code is shown (`echo=TRUE`); and
- the caption (`fig.cap`) as shown above.


## Digital Figures

Markdown, Pandoc and LaTeX support `.eps` and `.pdf` files.

Figures and Tables should be labelled and referenced in the standard way
using the `\label{}` and `\ref{}` commands.

The R examples above show how to insert a column-wide
figure. To insert a figure wider than one column, please use the
`\begin{figure*}...\end{figure*}` environment.

One (roundabout) way of doing this is to _not_ actually plot a figure, but to
save it in a file as the following segment shows:

```{r densityPlot, echo=TRUE}
library(ggplot2)
p <- ggplot(data = midwest,
            mapping = aes(x = area,
                          fill = state,
                          color = state)) +
    geom_density(alpha = 0.3)
## save to file
suppressMessages(ggsave("densities.pdf", p))
```

This file is then included via standard LaTeX commands.

\begin{figure*}
  \begin{center}
    \includegraphics[width=0.66\textwidth, height=3.5in]{densities}
  \end{center}
  \caption{Wide ggplot2 figure}\label{fig}
\end{figure*}


## Typeset Code (But Do Not Run It)

We can also just show code.

```r
xx <- faithful[,"eruptions"]
fit <- density(xx)
plot(fit)
```

This simply used a pandoc bloc started and ended by three backticks,
with `r` as the language choice.  Similarly, _many_ other languages
can be typeset directly simply by relying on pandoc.


## Single column equations

Authors may use 1- or 2-column equations in their article, according to
their preference.

To allow an equation to span both columns, options are to use the
`\begin{figure*}...\end{figure*}` environment mentioned above for
figures, or to use the `\begin{widetext}...\end{widetext}` environment
as shown in equation \ref{eqn:example} below.

Please note that this option may run into problems with floats and
footnotes, as mentioned in the [cuted package
documentation](http://texdoc.net/pkg/cuted). In the case of problems
with footnotes, it may be possible to correct the situation using
commands `\footnotemark` and `\footnotetext`.

\begin{equation}
  \begin{aligned}
(x+y)^3&=(x+y)(x+y)^2\\
       &=(x+y)(x^2+2xy+y^2) \\
       &=x^3+3x^2y+3xy^3+x^3.
       \label{eqn:example}
  \end{aligned}
\end{equation}


<!-- pandoc writes all tables using longtable, which fails in 2-column mode

  Species                    CBS     CV     G3
  ----------------------- ------ ------ ------
  1\. Acetaldehyde           0.0    0.0    0.0
  2\. Vinyl alcohol          9.1    9.6   13.5
  3\. Hydroxyethylidene     50.8   51.2   54.0

  : Comparison of the fitted potential energy surfaces and ab initio
  benchmark electronic energy calculations

-->

